Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-07-23 main.tex
start trafo

>>>>

\begin{proof}
    \begin{itemize}
    \item 
    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
    The mapping 
    \begin{align}
        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
    \end{align}
    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
    On the one hand, by the reverse triangle inequality,
    \begin{align}
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{y}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right\|
        \\&
        \geq 
        \left| 
            \frac{\|x\|}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{\|y\|}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \vec{1}
            \cdot 
            A^{-1}( x - y )
        \right|
     \end{align}
     Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$.

    \item 
    We let $S^{n}_{\star} := S^{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
    Suppose that $\bar x \in S^n$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
    We define its stereographic projection as 
    \begin{align}
        \pi( \bar x ) 
        = 
        \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
        .
    \end{align}
    This is a mapping $\pi : S^{n}_{\star} \rightarrow \bbR^{n}$. 
    Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
    \begin{align}
        \pi^{-1}( y )
        = 
        \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
        +
        \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
        .
    \end{align}
    \item 
    Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
    \begin{align}
        \mu : \bbR^{n} \rightarrow \bbR^{n},
        \qquad 
        y \mapsto \frac{y}{\| y \|}.
    \end{align}
    \item 
    \begin{align}
        G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
    \end{align}
    \item 
    \begin{align}
        F^{-1} \pi^{-1} G^{-1} \mu G \pi F
    \end{align}
    \end{itemize}
\end{proof}
